---
title: "Visualize Data"
output: html_notebook
---

```{r setup}
library(tidyverse)
```

```{r}
mpg
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))
```

## Your Turn 2

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class, size = cyl))
```

## Your Turn 3

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
ggplot(mpg) + geom_boxplot(aes(class, hwy))
```

## Your Turn 4

Make a histogram of the `hwy` variable from `mpg`.

```{r}
ggplot(mpg) +
  geom_histogram(aes(hwy), binwidth = 2)
```

## Your Turn 5

Make a density plot of `hwy` colored by `class`.

```{r}
ggplot(mpg) +
  geom_density(aes(hwy, color = class))
```

## Your Turn 6

Make a bar chart `hwy` colored by `class`.

```{r}
ggplot(mpg) +
  geom_bar(aes(class, fill = class))
```

## Your Turn 7

Predict what this code will do. Then run it.

```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point() +
  geom_smooth()
```

## Your Turn 8

What does `getwd()` return?

```{r}
getwd()
```

## Your Turn 9

Save the last plot and then locate it in the files pane.

```{r}
ggsave()
```

***

# Take aways

You can use this code template to make thousands of graphs with **ggplot2**.

```{r eval = FALSE}
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```